### 2016-06-16 paper/fig_dnf-regex-syntax.tex
responded to some feedback

% DNF_REGEX
(Atoms)& \Atom{},\AtomAlt{} & \GEq{} & \StarOf{\DNFRegex{}} & Iterate DNF\\
(Conjunct)& \Conjunct{},\ConjunctAlt{} & \GEq{} &
$\ConjunctOf{\String_0\ConjunctSep\Atom_1\ConjunctSep\ldots\ConjunctSep\Atom_n\ConjunctSep\String_n}$ & Conjoin\\
(DNF Regex)& \DNFRegex{},\DNFRegexAlt{} & \GEq{} & $\DNFOf{\Conjunct_1\DNFSep\ldots\DNFSep\Conjunct_n}$ & DNF Or\\
\end{tabular}
\caption{DNF Regex Syntax}
\label{fig:dnf-regex-syntax}
\end{figure}

>>>>

% DNF_REGEX
(Atoms)& \Atom{},\AtomAlt{} & \GEq{} & \StarOf{\DNFRegex{}} & Iterate DNF\\
(Sequence)& \Sequence{},\SequenceAlt{} & \GEq{} &
$\SequenceOf{\String_0\SequenceSep\Atom_1\SequenceSep\ldots\SequenceSep\Atom_n\SequenceSep\String_n}$ & Sequence\\
(DNF Regex)& \DNFRegex{},\DNFRegexAlt{} & \GEq{} & $\DNFOf{\Sequence_1\DNFSep\ldots\DNFSep\Sequence_n}$ & DNF Or\\
\end{tabular}
\caption{DNF Regex Syntax\bcp{Or how about ``hollow square
  brackets'' for conjuncts (using some kind of square brackets seems good,
  since they are ordered) and ``hollow set braces'' for disjuncts?  We
  should try to get this right, since these widgets are our core technical
  device.}} 
\label{fig:dnf-regex-syntax}
\end{figure}
